Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-05 Manuscript.Rmd
Replicated the permutation analysis from Matlab in R, with one caveat (see comments under 'Meta-analysis')

``` {r ROI computation from Matlab, echo=FALSE, message = FALSE}
# Based on Yeo et al. 17 network parcellation
# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
Yeo_labels <- c("_25_",
                "_OFC_",
                "_10v_",
                "_s32_",
                "_TE1a_",
                "_STSva_",
                "_8ad_",
                "_9p_",
                "_23d_",
                "_d23ab_",
                "_31a_",
                "_31pv_",
                "_31pd_",
                "_7m_",
                "_v23ab_",
                "_p24_",
                "_d32_",
                "_9m_",
                "_p32_",
                "_a24_",
                "_s32_",
                "_10r_",
                "_10d_",
                "_9a_",
                "_p10p_",
                "_PCV_",
                "_POS1_",
                "_RSC_")

@@

@@

# For each permutation, reassign the study labels, maintaining the original number of studies per condition 
allStudies <- c(studyList_sv, studyList_dmn)
nPerms <- 10
nullDist <- numeric()

@@

@@

}
```

>>>>

``` {r ROI computation from Matlab, echo=FALSE, message = FALSE}
# Based on Yeo et al. 17 network parcellation
# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
Yeo_labels <- c("L_25_",
                "L_OFC_",
                "L_10v_",
                "L_s32_",
                "L_TE1a_",
                "L_STSva_",
                "L_8ad_",
                "L_9p_",
                "L_23d_",
                "L_d23ab_",
                "L_31a_",
                "L_31pv_",
                "L_31pd_",
                "L_7m_",
                "L_v23ab_",
                "L_p24_",
                "L_d32_",
                "L_9m_",
                "L_p32_",
                "L_a24_",
                "L_10r_",
                "L_10d_",
                "L_9a_",
                "L_p10p_",
                "L_PCV_",
                "L_POS1_",
                "L_RSC_",
                "L_25_",
                "R_OFC_",
                "R_10v_",
                "R_s32_",
                "R_TE1a_",
                "R_STSva_",
                "R_8ad_",
                "R_9p_",
                "R_23d_",
                "R_d23ab_",
                "R_31a_",
                "R_31pv_",
                "R_31pd_",
                "R_7m_",
                "R_v23ab_",
                "R_p24_",
                "R_d32_",
                "R_9m_",
                "R_p32_",
                "R_a24_",
                "R_10r_",
                "R_10d_",
                "R_9a_",
                "R_p10p_",
                "R_PCV_",
                "R_POS1_",
                "R_RSC_")

@@

# This version is literally what I had selected originally, plus 25, OFC, 10v. This replicates the 7m finding. 
# But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
Yeo_labels <- c("L_25_",
                "L_OFC_",
                "L_10v_",
                "R_PGi_ROI",
                "R_PGs_ROI",
                "R_8Ad_ROI",
                "R_9p_ROI",
                "R_23d_ROI",
                "R_d23ab_RO",
                "R_31a_ROI",
                "R_31pv_ROI",
                "R_31pd_ROI",
                "R_7m_ROI",
                "R_v23ab_RO",
                "R_p24_ROI",
                "R_d32_ROI",
                "R_9m_ROI",
                "R_p32_ROI",
                "R_a24_ROI",
                "R_10r_ROI",
                "R_10d_ROI",
                "L_PGi_ROI",
                "L_PGs_ROI",
                "L_8Ad_ROI",
                "L_9p_ROI",
                "L_23d_ROI",
                "L_d23ab_RO",
                "L_31a_ROI",
                "L_31pv_ROI",
                "L_31pd_ROI",
                "L_7m_ROI",
                "L_v23ab_RO",
                "L_p24_ROI",
                "L_d32_ROI",
                "L_9m_ROI",
                "L_p32_ROI",
                "L_a24_ROI",
                "L_10r_ROI",
                "L_10d_ROI",
                "R_TE1a_ROI",
                "R_STSva_RO",
                "R_s32_ROI",
                "R_9a_ROI",
                "L_p10p_ROI",
                "L_PCV_ROI")

@@

# For each permutation, reassign the study labels, maintaining the original number of studies per condition 
allStudies <- c(studyList_sv, studyList_dmn)
nPerms <- 100
nullDist <- numeric()

@@

  if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}

@@

# Now do the same for the actual data, to see how it compares to the null dist
tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
                    SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
                    DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
                    propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
                    propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))

# Perform the prop test for each pair and get the max chi-squared stat
tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)})

plot(density(nullDist))

quantile(nullDist, 0.95)

tmpDF %>% filter(Chi_squared > quantile(nullDist,0.95))
```
